RNeXML: Parsing and Serializing the Next Generation of Phyloinformatic Data in R

### 2014-02-20 inst/doc/pubs/README.Rmd
working on check

@@

```{r echo=FALSE}
opts_knit$set(upload.fun = socialR::flickr.url)
opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, cache=TRUE)
```

@@

```{r}
f <- system.file("examples", "comp_analysis.xml", package="RNeXML")
nexml <- nexml_read(f)
tr <- get_tree(nexml) # or: as(nexml, "phylo")
plot(tr)
```

@@

```{r}
  nexml_write(bird.orders, 
              file = "example.xml", 
              additional_metadata = list(history, modified, website), 
              additional_namespaces = c(skos = "http://www.w3.org/2004/02/skos/core#",
                                        foaf = "http://xmlns.com/foaf/0.1/"))

@@

```{r}
nex <- add_trees(bird.orders)
nex <- nexml_taxize(nex)
```

@@

```{r}
library(RNeXML)
nexml <- read.nexml(system.file("examples", "comp_analysis.xml", package="RNeXML"))
traits <- get_characters_list(nexml)
tree <- get_tree(nexml)
```

@@

```{r}
library(geiger)
cts_model <- fitContinuous(tree, traits[[1]])
dct_model <- fitDiscrete(tree, traits[[2]])
```

>>>>

<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{An Introduction to the RNeXML package}
-->

@@

```{r echo=FALSE}
library(knitr)
opts_knit$set(upload.fun = socialR::flickr.url)
opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, cache=TRUE)
```

@@

```{r}
f <- system.file("examples", "comp_analysis.xml", package="RNeXML")
nexml <- nexml_read(f)
tr <- get_trees(nexml) # or: as(nexml, "phylo")
plot(tr[[1]])
```

@@

```{r}
  nexml_write(bird.orders, 
              file = "example.xml", 
              meta = list(history, modified, website), 
              namespaces = c(skos = "http://www.w3.org/2004/02/skos/core#",
                             foaf = "http://xmlns.com/foaf/0.1/"))

@@

```{r}
nex <- add_trees(bird.orders)
nex <- taxize_nexml(nex)
```

@@

```{r}
library(RNeXML)
nexml <- read.nexml(system.file("examples", "comp_analysis.xml", package="RNeXML"))
traits <- get_characters(nexml)
tree <- get_trees(nexml)
```

@@

```{r}
library(geiger)
fitContinuous(tree, traits[[1]])
fitDiscrete(tree, traits[[2]])
```
